---
title: "1-EDA"
author: "Janith Wanniarachchi"
date: "6/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
if(file.exists("data/train_data.csv")){
  train <- read_csv("data/train_data.csv")  
  test <- read_csv("data/test_data.csv")  
}else{
  train <- read_csv("../../data/train_data.csv")
  test <- read_csv("../../data/test_data.csv") 
}
```

Data Description

ID - unique ID given to an applicant
parents - occupation of parents (usual, pretentious, great_pret)
has_nurs - child's nursery (proper, less_proper, improper, critical, very_crit)
form - form of the family (complete, completed, incomplete, foster)
children - (children number (1, 2, 3, more)
housing - housing conditions (convenient, less_conv, critical)
finance - financial standing of the family (convenient, inconv)
social - social conditions (non-prob, slightly_prob, problematic)
health - health conditions (recommended, priority, not_recom)
app_status - label/target/response variable (1-selected, 0-not selected)

# Preprocessing steps

#### Convert app_status to factor
#### Convert character to factor
#### in the form column complete and completed have to be merged together

# Findings

#### No missing values

# Code

```{r}
skimr::skim(train)
```

```{r}
train %>% 
  mutate_if(is.character,factor) %>% 
  skimr::skim()
```

```{r}
train %>% 
  select_if(is.character) %>% 
  map(~ table(.x)/nrow(train))
```

```{r}
preprocess_data <- function(df,is_train = TRUE){
df <- df %>% 
  mutate_if(is.character,factor) %>% 
  
if(is_train){
df <- df %>% 
  mutate(app_status = factor(app_status,levels=c(0,1),labels=c("not selected","selected")))
}
}

  
```

